Methods to prioritise pop-up active transport infrastructure and their application in a national cycleway prioritisation tool

### 2020-06-23 article.Rmd
Minor fix in description of findings

The results of the method applied to the city of Leeds are shown in Figure \@ref(fig:res) (see [cyipt.bike/rapid](https://www.cyipt.bike/rapid/west-yorkshire/) for interactive version) and Table 2.
We found that analysis of open transport network data, alongside careful selection of parameters, can generate plausible results for the prioritisation of pop-up cycle infrastructure.
Reducing the 85,000 road segments for Leeds down to a handful of candidate segments with more than 1 lane near key destinations has great potential to support policy-makers, especially when decisions need to be made fast.

>>>>

The results of the method applied to the city of Leeds are shown in Figure \@ref(fig:res) (see [cyipt.bike/rapid](https://www.cyipt.bike/rapid/west-yorkshire/) for interactive version) and Table 2.
We found that analysis of open transport network data, alongside careful selection of parameters, can generate plausible results for the prioritisation of pop-up cycle infrastructure.
Reducing tens of thousands of road segments Leeds down to a handful of promising named road sections has great potential to support policy-makers, especially when decisions need to be made fast.

### 2020-06-23 article.tex
Minor fix in description of findings

The results of the method applied to the city of Leeds are shown in Figure \ref{fig:res} (see \href{https://www.cyipt.bike/rapid/west-yorkshire/}{cyipt.bike/rapid} for interactive version) and Table 2.
We found that analysis of open transport network data, alongside careful selection of parameters, can generate plausible results for the prioritisation of pop-up cycle infrastructure.
Reducing the 85,000 road segments for Leeds down to a handful of candidate segments with more than 1 lane near key destinations has great potential to support policy-makers, especially when decisions need to be made fast.

>>>>

The results of the method applied to the city of Leeds are shown in Figure \ref{fig:res} (see \href{https://www.cyipt.bike/rapid/west-yorkshire/}{cyipt.bike/rapid} for interactive version) and Table 2.
We found that analysis of open transport network data, alongside careful selection of parameters, can generate plausible results for the prioritisation of pop-up cycle infrastructure.
Reducing tens of thousands of road segments Leeds down to a handful of promising named road sections has great potential to support policy-makers, especially when decisions need to be made fast.
